Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage

### 2024-09-22 paper/paper.qmd
fix title

---
title: "Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage"
subtitle: "Insights from Toronto’s Fire Incidentsfinal"
author: 
  - Lexun Yu
thanks: "Code and data are available at: [https://github.com/yulexun/toronto-fire](https://github.com/yulexun/toronto-fire)."
date: today
date-format: long
abstract: "This paper analyzes fire incidents in Toronto between 2013 and 2023, focusing on the response times of the Toronto Fire Service (TFS) and the impact of fire protection systems. The study finds that TFS usually responds within 5 to 10 minutes, but the correlation between response time and financial losses is weak, and other factors like fire protection equipment play a larger role in mitigating damage. Fire alarms and sprinkler systems in present and operational reduce losses significantly. This research the importance of maintaining fire protection systems and improving fire service efficiency to enhance urban fire safety."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

>>>>

---
title: "Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage"
subtitle: "Insights from Toronto’s Fire Incidents"
author: 
  - Lexun Yu
thanks: "Code and data are available at: [https://github.com/yulexun/toronto-fire](https://github.com/yulexun/toronto-fire)."
date: today
date-format: long
abstract: "This paper analyzes fire incidents in Toronto between 2013 and 2023, focusing on the response times of the Toronto Fire Service (TFS) and the impact of fire protection systems. The study finds that TFS usually responds within 5 to 10 minutes, but the correlation between response time and financial losses is weak, and other factors like fire protection equipment play a larger role in mitigating damage. Fire alarms and sprinkler systems in present and operational reduce losses significantly. This research the importance of maintaining fire protection systems and improving fire service efficiency to enhance urban fire safety."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---
